\documentclass[
% hf, %% hf: enable header and footer.
]{ceurart}
%%
%% One can fix some overfulls
\sloppy

\input{packages}
\input{macro}

\begin{document}

%% Rights management information.
%% CC-BY is default license.
\copyrightyear{2025}
\copyrightclause{Copyright for this paper by its authors.
  Use permitted under Creative Commons License Attribution 4.0
  International (CC BY 4.0).}

%% This command is for the conference information
\conference{SMT 2025: 23rd International Workshop on Satisfiability Modulo Theories,
August 10--11, 2025, Glasgow, UK}

%% The "title" command
\title{CRTSolver: Solving Non-Linear Integer Equations using the Chinese Remainder Theorem}
\subtitle{An Extended Abstract}

%\tnotemark[1]
%\tnotetext[1]{Title note goes here}

\author[1]{Martin Brain}[%
orcid=0000-0003-4216-7151,
email=martin.brain@citystgeorges.ac.uk,
]
\address[1]{City St. George's, University of London,
  Northampton Square, London, EC1V 0HB, United Kingdom}

\author[1]{Maheen Matin}[%
orcid=0009-0005-8263-7041,
email=maheen.matin@city.ac.uk,
]

%\mmsays{We both have the same address, so please advise on the preferred format}
%\mbsays{Current set up is fine}

\begin{abstract}
 The SMT-LIB theory of integers allows for non-linear terms and is thus
 undecideable in the general case.
 %
 This is a practical problem but also discourages work on
 the decideable and easy fragments of the theory.
 %
 In this extended abstract we present a simple semi-decision procedure
 for sets of polynomial integer equations that shows significant promise
 in preliminary experiments with synthetic benchmarks.
 %
 We hope that this will illuminate the considerable improvements that
 are possible with well known techniques from the Diophantine equation and
 number theory literature.
\end{abstract}

\begin{keywords}
  Satisfiability modulo theories \sep
  Non-linear integer equations \sep
  Diophantine equations
\end{keywords}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle


\input{introduction}

\input{algorithm}

\input{results}

\input{conclusion}

%% The declaration on generative AI comes in effect
%% in Janary 2025. See also
%% https://ceur-ws.org/GenAI/Policy.html
\section*{Declaration on Generative AI}
  {\em Either:}\newline
  The author(s) have not employed any Generative AI tools.
  \newline
  
 \noindent{\em Or (by using the activity taxonomy in ceur-ws.org/genai-tax.html):\newline}
 During the preparation of this work, the author(s) used X-GPT-4 and Gramby in order to: Grammar and spelling check. Further, the author(s) used X-AI-IMG for figures 3 and 4 in order to: Generate images. After using these tool(s)/service(s), the author(s) reviewed and edited the content as needed and take(s) full responsibility for the publication’s content. 

\mbsays{We need to fill this out.  I haven't used any generative AI tools.}
 
%% Define the bibliography file to be used
\bibliography{CRTSolver}

%\appendix

\end{document}
